---
title: "p8105_hw1_ss6692"
output: html_document
date: "2023-09-22"
---
#P8015 Homework 1
```{r} 
library(tidyverse)
library(moderndive)
data("early_january_weather")
```
#Problem 1

Early January Weather describes weather details recorded at `EWR` using the `origin` variable from in `2013` from January `r min(early_january_weather$day)` to `r max(early_january_weather$day)`. Temperature is measured in Fahrenheit with the variable `temp`and values range from `r min(early_january_weather$temp)` to `r max(early_january_weather$temp)`. The variable `wind_speed` ranges from `r min(early_january_weather$wind_speed)` to `r max(early_january_weather$speed)` and humidity ranges from `r min(early_january_weather$humid)` to `r max(early_january_weather$humid)`.

The mean temperature is `r mean(early_january_weather$temp)`.

In this data set, there are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

```{r}
data.frame("early_january_weather")
x = early_january_weather$"time_hour"
y = early_january_weather$"temp"

ggplot(early_january_weather, aes(x = x, y = y, color=humid)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)

```


The variables `time_hour` and `temp` have an positive relationship. As the scatter plot shows, as time passes throughout the day, the temperature increases.







